How has the Brazilian Amazon been constructed as a problem? The economy, the environment, the people, and the nation in the presidential speeches since 1985

### 2022-05-16 Draft_April_2022/Full_draft_20220401.rmd
Updates to plots used in analysis sections according to feedback

```{r data, message=FALSE, warning=FALSE, include=FALSE}
pop<- readRDS("~/Documents/GitHub/amazondef/Replication_files/BR_presid_speeches_final.Rds")
pop <-  pop %>% select(-c(title, date, text, location))
ama <- readRDS("~/Documents/GitHub/amazondef/Replication_files/final_data_as.Rds")
ama <-  ama %>% select(-c(title, date, text, false_positives)) %>% rename (ei= "EI", sd= "SD")
AAI <- readRDS("~/Documents/GitHub/amazondef/Replication_files//AAI.Rds")
amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/Replication_files//amazon_def_year.Rds")
```

```{r data prep for prob_construction, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
sov <- ama %>% 
  filter(sov==1) %>% 
  count(sov, year) %>%
  group_by(year) %>%
  select(-c(sov))%>%
  rename (sov = n)
ei <- ama %>% 
  filter(ei==1) %>% 
  count(ei, year) %>%
  group_by(year) %>%
  select(-c(ei))%>%
  rename (ei = n) %>%
  ungroup() %>%
  tibble::add_row(year = 2017, ei = 0) %>%
  tibble::add_row(year = 2018, ei = 0)
sd <- ama %>% 
  filter(sd==1) %>% 
  count(sd, year) %>%
  group_by(year) %>%
  select(-c(sd))%>%
  rename (sd = n)
con <- ama %>% 
  filter(con==1) %>% 
  count(con, year) %>%
  group_by(year) %>%
  select(-c(con))%>%
  rename (con = n)
other <- ama %>% 
  filter(other==1) %>% 
  count(other, year) %>%
  group_by(year) %>%
  select(-c(other))%>%
  rename (other = n)
temp <- ei %>% left_join(other) %>% 
                left_join(con) %>%
                left_join(sd) %>%
                left_join(sov) %>%
                replace(is.na(.), 0)
```

```{r data prep for mixed_types, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
ama_mx <-  ama %>%
  unite(mixed_type, sov:con, sep="_") %>%
  mutate(mx_cat = factor(case_when(mixed_type == '1_0_0_0' ~ "Pure Sovereignty",
                                      mixed_type == '0_1_0_0' ~ "Pure Economic Integration", 
                                      mixed_type == '0_0_1_0' ~ "Pure Social Development",
                                      mixed_type == '0_0_0_1' ~ "Pure Conservation",
                                      mixed_type == '0_0_0_0' ~ "Other",
                                      mixed_type == '0_1_0_1' ~ "Economic Conservation",
                                      mixed_type == '0_1_1_0' ~ "Economic and Social Development",
                                      mixed_type == '1_0_0_1' ~ "Sovereign Conservation",
                                      mixed_type == '0_1_1_1' ~ "Sustainable Development",
                                      mixed_type == '1_1_0_0' ~ "Sovereign Integration",
                                      mixed_type == '0_0_1_1' ~ "Social Conservation",
                                      grepl("1_0_1_0|1_0_1_0|1_0_1_1|1_1_0_1|1_1_1_0|1_1_1_1",
                                            mixed_type) ~ "Other Mixed-types"),
         levels = c("Pure Economic Integration", "Pure Conservation", "Pure Social Development",
                    "Pure Sovereignty", "Other", "Economic Conservation", "Economic and Social Development",
                    "Sovereign Conservation","Sustainable Development","Sovereign Integration",
                    "Social Conservation", "Other Mixed-types")),
         mx_cat2 = case_when(grepl("Pure Economic Integration|Pure Conservation|
                                   |Pure Social Development|Pure Sovereignty", mx_cat) ~ "Pure-types",
                             grepl("^Other$", mx_cat) ~ "Other",
                             grepl("Economic Conservation|Economic and Social Development|
                                   |Sovereign Conservation|Sustainable Development|
                                   |Sovereign Integration|Social Conservation|Other Mixed-types",
                                   mx_cat) ~ "Mixed-types"))
```

@@

```{r Figure 1: Amazonian speeches by year, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
perc1 <- pop %>%
  count(amazon_speech, year)%>%
  group_by(year)%>%
  mutate(perc=n / sum(n)) %>%
  select(c(perc,amazon_speech, year))
pop2 <- pop %>% count(amazon_speech, year, president) %>%
  group_by(year, president) %>%
  left_join(perc1) %>%
  filter(amazon_speech==1)
pop2 <- left_join(pop2, AAI, by = "year")
pop2 <- left_join(pop2, amazon_def_year, by = "year")
model <- lm(perc ~ AAI+ def_year + president, data=pop2)
pop2$predicted = predict(model, pop2)
Amazon_year <- pop2 %>% ggplot(., aes(x = year, y = perc)) +
  geom_line(size=.85, aes(x=year, y=perc, color="Real share")) +
  geom_line(size=.45, aes(x=year, y=predicted, color= "Predicted share")) +
  geom_text(aes(x = 1988, y = 0.34, label = "Chico Mendes/NYT"), size = 3) +
  geom_vline(xintercept = 1988, linetype="dotted") +
  geom_text(aes(x = 1992, y = 0.27, label = "Earth Summmit"), size = 3) + 
  geom_vline(xintercept = 1992, linetype="dotted") +
  geom_text(aes(x = 2009, y = 0.25, label = "Copenhagen Summmit"), size = 3) + 
  geom_vline(xintercept = 2009, linetype="dotted") +
  geom_text(aes(x = 2015, y = 0.21, label = "Paris Summmit"), size = 3) + 
  geom_vline(xintercept = 2015, linetype="dotted") +
  scale_color_manual(values = c("Real share" = "darkolivegreen", "Predicted share" = "gray40")) +
  scale_y_continuous(labels = percent_format()) +
  labs(x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
       subtitle = "Sample composed by 6130 presidential speeches since 1985",
       caption = "Predicted share controls for deforestation rates, inflation, and president.",
       color='Y series') +
  theme(panel.background = element_rect("white", "black", .5, "solid"),
        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
        axis.text = element_text(color = "black", size = 10),
        title = element_text(color = "black", size = 10, face = "bold"),
        legend.title = element_blank(),
        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
        legend.position = "bottom")
Amazon_year
```

@@

```{r Figure 3: pure types in time , echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
pure_types_time <- ama_mx %>%
  count(mx_cat, mx_cat2, year) %>%
  group_by(year) %>%
  mutate(perc = n / sum(n)) %>% 
  filter(mx_cat2 == "Pure-types") %>% 
  ggplot(aes(x=as.numeric(year), y = perc, color = mx_cat)) +
  geom_smooth(aes(fill = mx_cat), size = .5) +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = "", y = "", title ="Share of each pure type by year",
       subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
       caption = "") +
  theme(panel.background = element_rect("white", "black", .5, "solid"),
        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
        axis.text = element_text(color = "black", size = 10),
        title = element_text(color = "black", size = 10, face = "bold"),
        legend.title = element_blank(),
        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
        legend.position = "bottom")
pure_types_time
```

@@

```{r Figure 4: mixed-types by president , echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
mixed_types_presid <- ama_mx %>%
  filter(mx_cat2 == "Mixed-types") %>%
  count(president, mx_cat) %>%
  group_by(president) %>%
  mutate(perc = n / sum(n)) %>%
  mutate(president = factor(president,
                            levels = c("Sarney", "Collor", "Itamar", "FHC", "Lula", "Dilma", "Temer", "Bolsonaro"))) %>%
  ggplot(aes(x=president, y=perc, fill=mx_cat,label= scales::percent(perc, accuracy=.1))) +
  geom_bar(stat="identity", position="stack") +
  geom_text(size = 3, position = position_stack(vjust=.5)) +
  scale_fill_brewer(type = "qual", palette = "Set2", direction= 1) +
  labs(x = "", y = "", title ="Share of each mixed type problem-constructions by president",
       subtitle = "Sample composed of Amazonian statements that were coded as a mixed-type (n=431)",
       caption = "") +
  theme(panel.background = element_rect("white", "black", .5, "solid"),
        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
        axis.text = element_text(color = "black", size = 10),
        title = element_text(color = "black", size = 10, face = "bold"),
        legend.title = element_blank(),
        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
        legend.position = "bottom")
mixed_types_presid
```

We also observe the comeback of sovereignty being used in mixed types, mostly in detriment of conservation social development. This becomes more apparent in a comparison between Lula and Bolsonaro, the two presidents that mix the most with proportions more than 11% above presidential averages: 29.4% and 31.3% respectively. While the former frequently mixed conservation with other problem constructions, the latter prefers mixing with sovereignty. The combination of sovereignty with economic integration, which was also characteristic of the military dictatorship policies for the region, reaches its highest level with Bolsonaro: 22.7% of all mixed types. Now that we've inspected and de veloped pure and mixed types, we can check if these specific problem constructions vary depending on where the president is speaking.

@@

```{r multimonial model, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
adr <- data.frame(year = c(1985, 1986, 1987), def_year = c(21.050, 21.050, 21.050))
amazon_def_year <- rbind(adr, amazon_def_year)
ama_model <- dplyr::left_join(ama_mx, amazon_def_year, by = "year") # merge
ama_model <- dplyr::left_join(ama_model, AAI, by = "year") # merge
ama_model <- filter(ama_model, location_cat != "Non Identified", mx_cat != "Other Mixed-types") %>% 
  mutate(mx_cat = factor(mx_cat, levels = c("Pure Conservation", "Pure Economic Integration",
                                            "Pure Social Development", "Pure Sovereignty", "Economic Conservation",
                                            "Economic and Social Development", "Sovereign Conservation",
                                            "Sustainable Development","Sovereign Integration",
                                            "Social Conservation", "Other")),
         election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018", year), 1, 0))
# model
model <- multinom(mx_cat ~ location_cat + election_year + def_year + AAI, data = ama_model, model = TRUE, trace = FALSE)
# summary statistics
model_summary <- summary(model)
p_values <- round((1 - pnorm(abs(summary(model)$coefficients/summary(model)$standard.errors)))*2, 5)

# too much information... Let's just focus on what we want here...
md <- tibble("Dependent Variable" = c("Economic Integration vs Environmental Conservation",
                                           "Social Development vs Environmental Conservation",
                                           "Sovereignty vs Environmental Conservation"),
                 "Brasilia vs Amazonian States" = c("-1.024*** (0.169)","-1.002*** (0.205)", "-0.206 (0.260)"),
                 "International vs Amazonian States" = c("-0.612*** (0.192)", "-1.583*** (0.303)", "-1.427*** (0.431)"),
                 "Other States vs Amazonian States" = c("0.023 (0.197)", "-0.041 (0.230)", "0.324 (0.302)"),
                 "Election Year" = c("-0.241 (0.186)", "0.028 (0.215)", "-0.684** (0.298)"),
                 "Annual Deforestation" = c("0.063*** (0.013)", "-0.031* (0.016)", "0.004 (0.019)"),
                 "Average Inflation" = c("-0.001*** (0.0001)", "-0.001*** (0.0002)", "-0.0001 (0.0002)"))

>>>>

```{r data, message=FALSE, warning=FALSE, include=FALSE}
# Load data
pop<- readRDS("~/Documents/GitHub/amazondef/Replication_files/BR_presid_speeches_final.Rds")
pop <-  pop %>% select(-c(title, date, text, location))
ama <- readRDS("~/Documents/GitHub/amazondef/Replication_files/final_data_as.Rds")
ama <-  ama %>% select(-c(title, date, text, false_positives)) %>% rename (ei= "EI", sd= "SD")
AAI <- readRDS("~/Documents/GitHub/amazondef/Replication_files//AAI.Rds")
amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/Replication_files//amazon_def_year.Rds")
# Prepare data for problem constructions
sov <- ama %>% 
  filter(sov==1) %>% 
  count(sov, year) %>%
  group_by(year) %>%
  select(-c(sov))%>%
  rename (sov = n)
ei <- ama %>% 
  filter(ei==1) %>% 
  count(ei, year) %>%
  group_by(year) %>%
  select(-c(ei))%>%
  rename (ei = n) %>%
  ungroup() %>%
  tibble::add_row(year = 2017, ei = 0) %>%
  tibble::add_row(year = 2018, ei = 0)
sd <- ama %>% 
  filter(sd==1) %>% 
  count(sd, year) %>%
  group_by(year) %>%
  select(-c(sd))%>%
  rename (sd = n)
con <- ama %>% 
  filter(con==1) %>% 
  count(con, year) %>%
  group_by(year) %>%
  select(-c(con))%>%
  rename (con = n)
other <- ama %>% 
  filter(other==1) %>% 
  count(other, year) %>%
  group_by(year) %>%
  select(-c(other))%>%
  rename (other = n)
temp <- ei %>% 
  left_join(other) %>% 
  left_join(con) %>% 
  left_join(sd) %>% 
  left_join(sov) %>% 
  replace(is.na(.), 0)
# Get mixed types in
ama_mx <-  ama %>%
  unite(mixed_type, sov:con, sep="_") %>%
  mutate(mx_cat = factor(case_when(mixed_type == '1_0_0_0' ~ "Pure Sovereignty",
                                      mixed_type == '0_1_0_0' ~ "Pure Economic Integration", 
                                      mixed_type == '0_0_1_0' ~ "Pure Social Development",
                                      mixed_type == '0_0_0_1' ~ "Pure Conservation",
                                      mixed_type == '0_0_0_0' ~ "Other",
                                      mixed_type == '0_1_0_1' ~ "Economic Conservation",
                                      mixed_type == '0_1_1_0' ~ "Economic and Social Development",
                                      mixed_type == '1_0_0_1' ~ "Sovereign Conservation",
                                      mixed_type == '0_1_1_1' ~ "Sustainable Development",
                                      mixed_type == '1_1_0_0' ~ "Sovereign Integration",
                                      mixed_type == '0_0_1_1' ~ "Social Conservation",
                                      grepl("1_0_1_0|1_0_1_0|1_0_1_1|1_1_0_1|1_1_1_0|1_1_1_1",
                                            mixed_type) ~ "Other Mixed-types"),
         levels = c("Pure Economic Integration", "Pure Conservation", "Pure Social Development",
                    "Pure Sovereignty", "Other", "Economic Conservation", "Economic and Social Development",
                    "Sovereign Conservation","Sustainable Development","Sovereign Integration",
                    "Social Conservation", "Other Mixed-types")),
         mx_cat2 = case_when(grepl("Pure Economic Integration|Pure Conservation|
                                   |Pure Social Development|Pure Sovereignty", mx_cat) ~ "Pure-types",
                             grepl("^Other$", mx_cat) ~ "Other",
                             grepl("Economic Conservation|Economic and Social Development|
                                   |Sovereign Conservation|Sustainable Development|
                                   |Sovereign Integration|Social Conservation|Other Mixed-types",
                                   mx_cat) ~ "Mixed-types"),
         election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018", year), 1, 0))
```

@@

```{r Figure 1: Amazonian speeches by year, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
perc1 <- pop %>%
  count(amazon_speech, year) %>%
  group_by(year) %>%
  mutate(perc=n / sum(n)) %>%
  filter(amazon_speech == 1) %>% 
  select(c(perc, amazon_speech, year))
######## We have an issue with data here btw, 1992 only has 4 obs in the population... #######
######## Issue is with biblioteca presidencial, not with scarping btw ######
# summary(as.factor(pop$year))
# Simple plot
Amazon_year <- perc1 %>% ggplot(., aes(x = year, y = perc)) +
  geom_line(color = "darkgreen") +
  scale_y_continuous(labels = percent_format()) +
  geom_text(aes(x = 1988, y = 0.34, label = "Chico Mendes/NYT"), size = 3) +
  geom_text(aes(x = 1992, y = 0.27, label = "Earth Summit"), size = 3) +
  geom_text(aes(x = 2009, y = 0.24, label = "Copenhagen Summit"), size = 3) +
  geom_text(aes(x = 2015, y = 0.21, label = "Paris Summit"), size = 3) +
  geom_vline(xintercept = c(1988, 1992, 2009, 2015),
             linetype = "dotted") +
  labs(x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
       subtitle = "Sample composed by 6130 presidential speeches since 1985",
       caption = "",
       color='Y series') +
  theme(panel.background = element_rect("white", "black", .5, "solid"),
        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
        axis.text = element_text(color = "black", size = 10),
        title = element_text(color = "black", size = 10, face = "bold"),
        legend.title = element_blank(),
        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
        legend.position = "bottom")
# # # With a few lines under the
# cat1 <- ama_mx %>%
#   mutate(cat = ifelse(mx_cat2 == "Mixed-types", "Mixed-types", paste(mx_cat))) %>%
#   count(cat, year) %>%
#   group_by(year) %>%
#   mutate(perc = n / sum(n),
#          perc_type = ifelse(perc == 1, 0.25, perc)) %>% 
#   arrange(year) %>%
#   select(c(cat, year, perc_type))
# year_share <- merge(perc1, cat1, "year") %>%
#   mutate(year_perc = perc*perc_type)
# Amazon_year <- year_share %>% ggplot(., aes(x = year, y = perc)) +
#   geom_line(aes(y = perc)) +
#   scale_y_continuous(labels = percent_format()) +
#   geom_line(aes(x = year, y = year_perc, fill = cat, group = cat, color = cat)) +
#   geom_text(aes(x = 1988, y = 0.34, label = "Chico Mendes/NYT"), size = 3) +
#   geom_text(aes(x = 1992, y = 0.27, label = "Earth Summit"), size = 3) +
#   geom_text(aes(x = 2009, y = 0.24, label = "Copenhagen Summit"), size = 3) +
#   geom_text(aes(x = 2015, y = 0.21, label = "Paris Summit"), size = 3) +
#   geom_vline(xintercept = c(1988, 1992, 2009, 2015),
#              linetype = "dotted") +
#   labs(x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
#        subtitle = "Sample composed by 6130 presidential speeches since 1985",
#        caption = "",
#        color='Y series') +
#   theme(panel.background = element_rect("white", "black", .5, "solid"),
#         panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
#         axis.text = element_text(color = "black", size = 10),
#         title = element_text(color = "black", size = 10, face = "bold"),
#         legend.title = element_blank(),
#         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
#         legend.position = "bottom")
# # For filling the area under the line
# Amazon_year <- year_share %>% ggplot(., aes(x = year, y = year_perc, fill = cat)) +
#   geom_line() +
#   geom_area() +
#   scale_y_continuous(labels = percent_format()) +
#   geom_text(aes(x = 1988, y = 0.34, label = "Chico Mendes/NYT"), size = 3) +
#   geom_vline(xintercept = 1988, linetype = "dotted") +
#   geom_text(aes(x = 1992, y = 0.27, label = "Earth Summit"), size = 3) +
#   geom_vline(xintercept = 1992, linetype = "dotted") +
#   geom_text(aes(x = 2009, y = 0.25, label = "Copenhagen Summit"), size = 3) +
#   geom_vline(xintercept = 2009, linetype = "dotted") +
#   geom_text(aes(x = 2015, y = 0.21, label = "Paris Summit"), size = 3) +
#   geom_vline(xintercept = 2015, linetype = "dotted") +
#   labs(x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
#        subtitle = "Sample composed by 6130 presidential speeches since 1985",
#        caption = "",
#        color = 'Y series') +
#   theme(panel.background = element_rect("white", "black", .5, "solid"),
#         panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
#         axis.text = element_text(color = "black", size = 10),
#         title = element_text(color = "black", size = 10, face = "bold"),
#         legend.title = element_blank(),
#         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
#         legend.position = "bottom")
# # Controling for inflation and deforastation
# pop2 <- pop %>% count(amazon_speech, year, president) %>%
#   group_by(year, president) %>%
#   left_join(perc1) %>%
#   filter(amazon_speech==1)
# pop2 <- left_join(pop2, AAI, by = "year")
# pop2 <- left_join(pop2, amazon_def_year, by = "year")
# model <- lm(perc ~ AAI+ def_year + president, data=pop2)
# pop2$predicted = predict(model, pop2)
# Amazon_year <- pop2 %>% ggplot(., aes(x = year, y = perc)) +
#   geom_line(size=.85, aes(x=year, y=perc, color="Real share")) +
#   geom_line(size=.45, aes(x=year, y=predicted, color= "Predicted share")) +
#   geom_text(aes(x = 1988, y = 0.34, label = "Chico Mendes/NYT"), size = 3) +
#   geom_vline(xintercept = 1988, linetype="dotted") +
#   geom_text(aes(x = 1992, y = 0.27, label = "Earth Summit"), size = 3) + 
#   geom_vline(xintercept = 1992, linetype="dotted") +
#   geom_text(aes(x = 2009, y = 0.25, label = "Copenhagen Summit"), size = 3) + 
#   geom_vline(xintercept = 2009, linetype="dotted") +
#   geom_text(aes(x = 2015, y = 0.21, label = "Paris Summit"), size = 3) + 
#   geom_vline(xintercept = 2015, linetype="dotted") +
#   scale_color_manual(values = c("Real share" = "darkolivegreen", "Predicted share" = "gray40")) +
#   scale_y_continuous(labels = percent_format()) +
#   labs(x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
#        subtitle = "Sample composed by 6130 presidential speeches since 1985",
#        caption = "Predicted share controls for deforestation rates, inflation, and president.",
#        color='Y series') +
#   theme(panel.background = element_rect("white", "black", .5, "solid"),
#         panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
#         axis.text = element_text(color = "black", size = 10),
#         title = element_text(color = "black", size = 10, face = "bold"),
#         legend.title = element_blank(),
#         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
#         legend.position = "bottom")
Amazon_year

@@

```{r Figure 3: pure types in time , echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
hp = data.frame(beg = c(1985, 1990, 1993, 1994, 2002, 2010, 2016, 2018),
                end = c(1990, 1993, 1994, 2002, 2010, 2016, 2018, 2022),
                label = c(1987, 1991, 1993, 1998, 2006, 2013, 2017, 2020),
                presid = c("Sarney", "Collor", "Franco", "Cardoso", "Lula",
                           "Rousseff", "Temer", "Bolsonaro"))
pure_types_time <- ama_mx %>%
  count(mx_cat, mx_cat2, year) %>%
  group_by(year) %>%
  mutate(perc = n / sum(n)) %>% 
  filter(mx_cat2 == "Pure-types") %>% 
  ggplot(aes(x=as.numeric(year), y = perc, color = mx_cat)) +
  geom_smooth(aes(fill = mx_cat), se = FALSE, size = .5) + # to add CI here set se to TRUE
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = "", y = "", title ="Share of each pure type by year",
       subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
       caption = "") +
  theme(panel.background = element_rect("white", "black", .5, "solid"),
        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
        axis.text = element_text(color = "black", size = 10),
        title = element_text(color = "black", size = 10, face = "bold"),
        legend.title = element_blank(),
        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
        legend.position = "bottom") +
  annotate(geom = "rect", xmin = hp$beg, xmax = hp$end, ymin = 0, ymax = 0.44,
           fill = c("mediumpurple4", "mediumorchid1", "mediumpurple4", "mediumorchid1",
                    "mediumpurple4", "mediumorchid1", "mediumpurple4", "mediumorchid1"),
           alpha = 0.1) +
  annotate(geom = "text", x = hp$label, y = 0.4, angle = 40,
           label = hp$presid, alpha = 0.4)
pure_types_time
```

@@

```{r Figure 4: mixed-types by president , echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
mixed_types_presid <- ama_mx %>%
  count(president, mx_cat, mx_cat2) %>%
  group_by(president) %>%
  mutate(perc = n / sum(n)) %>% 
  filter(mx_cat2 == "Mixed-types") %>% 
  mutate(president = factor(president, levels = c("Sarney", "Collor", "Itamar", "FHC",
                                                  "Lula", "Dilma", "Temer", "Bolsonaro"))) %>%
  ggplot(aes(x = president, y = perc, fill = mx_cat,
             label = scales::percent(perc, accuracy=.1))) +
  geom_bar(stat = "identity", position = "stack") +
  geom_text(size = 3, position = position_stack(vjust = .5)) +
  scale_fill_brewer(type = "qual", palette = "Set2", direction= 1) +
  labs(x = "", y = "", title ="Share of each mixed type problem-constructions by president",
       subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
       caption = "") +
  theme(panel.background = element_rect("white", "black", .5, "solid"),
        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
        axis.text = element_text(color = "black", size = 10),
        title = element_text(color = "black", size = 10, face = "bold"),
        legend.title = element_blank(),
        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
        legend.position = "bottom")
mixed_types_presid
```

We also observe the comeback of sovereignty being used in mixed types, mostly in detriment of conservation social development. This becomes more apparent in a comparison between Lula and Bolsonaro, the two presidents that mix the most with proportions more than 11% above presidential averages: 29.4% and 31.3% respectively. While the former frequently mixed conservation with other problem constructions, the latter prefers mixing with sovereignty. The combination of sovereignty with economic integration, which was also characteristic of the military dictatorship policies for the region, reaches its highest level with Bolsonaro: 22.7% of all mixed types. Now that we've inspected and developed pure and mixed types, we can check if these specific problem constructions vary depending on where the president is speaking.

@@

```{r multimonial model, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
adr <- data.frame(year = c(1985, 1986, 1987), def_year = c(21.050, 21.050, 21.050))
amazon_def_year <- rbind(adr, amazon_def_year)
ama_model <- dplyr::left_join(ama_mx, amazon_def_year, by = "year") # merge
ama_model <- dplyr::left_join(ama_model, AAI, by = "year") # merge
ama_model <- filter(ama_model, location_cat != "Non Identified", mx_cat != "Other Mixed-types") %>% 
  mutate(mx_cat = factor(mx_cat, levels = c("Pure Conservation", "Pure Economic Integration",
                                            "Pure Social Development", "Pure Sovereignty",
                                            "Economic Conservation",
                                            "Economic and Social Development", "Sovereign Conservation",
                                            "Sustainable Development","Sovereign Integration",
                                            "Social Conservation", "Other")))
# model
model <- multinom(mx_cat ~ location_cat + election_year + def_year + AAI,
                  data = ama_model, model = TRUE, trace = FALSE)
# summary statistics
model_summary <- summary(model)
p_values <- round((1 - pnorm(abs(summary(model)$coefficients/summary(model)$standard.errors)))*2, 5)
# Independence of Irrelevant Alternatives (Hausman-McFadden) test, in practice
iia_data <- filter(ama_model, mx_cat != "Pure Economic Integration")
iia <- multinom(mx_cat ~ location_cat + election_year + def_year + AAI,
                data = iia_data, model = TRUE, trace = FALSE)
iia_summary <- summary(iia)
iia_p_values <- round((1 - pnorm(abs(summary(iia)$coefficients/summary(iia)$standard.errors)))*2, 5)
# Model coefficients, and p-values, are statistically identical even when we drop the largest
# factor category from model. Therefore, we can proceed with a multinomial logit model,
# instead of a multinomial probit model, since the independence of irrelevant alternatives 
# Other post estimation tests
chi_square <- chisq.test(ama_model$mx_cat, predict(model)) 
# Chi-square p value (p-value < 0.001) tells us that our model explains a
# significant amount of the variation in the data in comparison with a null model.
# But too much information on the summary tables... Let's just focus on what we want here:
md <- tibble("Dependent Variable" = c("Economic Integration vs Environmental Conservation",
                                           "Social Development vs Environmental Conservation",
                                           "Sovereignty vs Environmental Conservation"),
                 "Brasilia vs Amazonian States" = c("-1.024*** (0.169)","-1.002*** (0.205)", "-0.206 (0.260)"),
                 "International vs Amazonian States" = c("-0.612*** (0.192)", "-1.583*** (0.303)", "-1.427*** (0.431)"),
                 "Other States vs Amazonian States" = c("0.023 (0.197)", "-0.041 (0.230)", "0.324 (0.302)"),
                 "Election Year" = c("-0.241 (0.186)", "0.028 (0.215)", "-0.684** (0.298)"),
                 "Annual Deforestation" = c("0.063*** (0.013)", "-0.031* (0.016)", "0.004 (0.019)"),
                 "Average Inflation" = c("-0.001*** (0.0001)", "-0.001*** (0.0002)", "-0.0001 (0.0002)"))
